\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in,right=0.75in,top=0.75in,bottom=0.75in]{geometry}
\usepackage{graphicx}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{mathptmx} % Times New Roman font

\pagenumbering{gobble} % Remove page numbers

% Section formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

% List formatting
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt}

\begin{document}

% Header
\begin{minipage}[t]{0.65\textwidth}
    \begin{minipage}[c]{0.2\textwidth}
        % Placeholder for Logo
        \framebox[2cm][c]{\rule{0pt}{2cm}Logo} 
    \end{minipage}
    \begin{minipage}[c]{0.75\textwidth}
        {\LARGE \textbf{OMI CHAUHAN}} \\[2pt]
        Roll No.: 23MMB0A31 \\
        B.Tech in Metallurgy and Material Sciences \\
        National Institute of Technology, Warangal
    \end{minipage}
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
    \raggedleft
    \small
    \faPhone\ +91-9770845401 \\
    \faEnvelope\ \href{mailto:oc23mmb0a31@student.nitw.ac.in}{oc23mmb0a31@student.nitw.ac.in} \\
    \faEnvelope\ \href{mailto:omichauhan427@gmail.com}{omichauhan427@gmail.com} \\
    \faGithub\ \href{https://github.com/omichauhan-lgtm}{omichauhan-lgtm} \\
    \faLinkedin\ \href{https://www.linkedin.com/in/omichauhan/}{omichauhan}
\end{minipage}

\vspace{10pt}

% Education
\section*{EDUCATION}
\begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{National Institute of Technology, Warangal} & 2023 -- 2027 \\
    \textit{B.Tech in Metallurgy and Material Sciences} & \\
    \multicolumn{2}{c}{} \\
    \textbf{Central Board of Secondary Education (Class XII)} & 2022 \\
    \textit{Higher Secondary} & 96\% \\
    \multicolumn{2}{c}{} \\
    \textbf{Central Board of Secondary Education (Class X)} & 2020 \\
    \textit{Secondary School} & 93\% \\
\end{tabularx}

% Experience - MODIFIED FOR CADP (Business Intelligence focus)
\section*{EXPERIENCE}
\textbf{Rajputana Vehicles Pvt. Ltd.} \hfill May 2025 -- June 2025 \\
\textit{Data Analyst Intern (Business Intelligence)} \hfill Madhya Pradesh, India
\begin{itemize}
    \item Designed Business Intelligence (BI) dashboards to track Key Performance Indicators (KPIs) for sales regions.
    \item Conducted customer segmentation analysis to drive 15\% more targeted marketing strategies.
    \item Collaborated with senior management to translate complex data into actionable business reports.
    \item Utilized Python and Excel to automate weekly reporting processes, reducing manual effort by 40\%.
\end{itemize}

% Personal Projects
\section*{PERSONAL PROJECTS}
\textbf{AutoSight SaaS} \hfill 2024 \\
\textit{B2B Automotive Market Analytics Platform}
\begin{itemize}
    \item \textbf{Tools \& Technologies:} React, SQL, Data Analytics, KPI Dashboarding
    \item Developed a B2B SaaS product helping automotive dealers understand market demand.
    \item Created visual reports and forecasting tools to assist businesses in inventory planning.
    \item Integrated multi-tenant architecture to support multiple business clients simultaneously.
\end{itemize}

\vspace{5pt}

\textbf{Credit Risk Intelligence} \hfill 2024 \\
\textit{Automated Credit Risk Assessment SaaS}
\begin{itemize}
    \item \textbf{Tools \& Technologies:} Python, Streamlit, Machine Learning (Scikit-learn)
    \item Developed a financial risk assessment tool to predict borrower default potential.
    \item Created executive-level dashboards for visualizing portfolio risk distribution.
\end{itemize}

\vspace{5pt}

\textbf{Gridiron Tactics Engine} \hfill 2024 \\
\textit{C++ Game Architecture Simulation (EA Sports)}
\begin{itemize}
    \item \textbf{Tools \& Technologies:} C++, STL, Object-Oriented Design, System Architecture
    \item Built a console-based strategy game engine simulating professional football tactical preparation.
    \item Implemented complex systems integration, connecting a gameplay loop (Film Room) with a persistent economy (Inventory).
    \item Optimized performance using modern C++ memory management (smart pointers and vectors) replacing legacy structures.
\end{itemize}

% Technical Skills - MODIFIED FOR CADP
\section*{TECHNICAL SKILLS AND INTERESTS}
\begin{itemize}
    \item \textbf{Languages:} Python, SQL, JavaScript
    \item \textbf{Business Tools:} Power BI, Excel (Advanced), Streamlit (Dashboards)
    \item \textbf{Competencies:} Data Analysis, Business Intelligence, Strategic Planning, KPI Tracking
    \item \textbf{Areas of Interest:} Corporate Strategy, FinTech Products, Business Analytics
\end{itemize}

% Positions of Responsibility
\section*{POSITIONS OF RESPONSIBILITY}
\textbf{PR Team Head, Technozion} \hfill 2023 -- 2024 \\
\textit{Technical Fest, NIT Warangal}
\begin{itemize}
    \item Led the Public Relations team for one of South India's largest technical fests.
\end{itemize}

\vspace{5pt}

\textbf{Sponsorship Team Head, Springspree} \hfill 2023 -- 2024 \\
\textit{Cultural Fest, NIT Warangal}
\begin{itemize}
    \item Managed corporate sponsorships and partnerships for the annual cultural fest.
\end{itemize}

% Achievements
\section*{ACHIEVEMENTS}
\begin{itemize}
    \item \textbf{JPMorgan Chase Forage Virtual Internship:} Gained practical experience in software engineering and fintech.
\end{itemize}

\end{document}
