\documentclass[a4paper,10pt]{article}
\usepackage[left=0.75in,right=0.75in,top=0.75in,bottom=0.75in]{geometry}
\usepackage{graphicx}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{mathptmx} % Times New Roman font

\pagenumbering{gobble} % Remove page numbers

% Section formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

% List formatting
\setlist[itemize]{leftmargin=*, noitemsep, topsep=0pt}

\begin{document}

% Header
\begin{minipage}[t]{0.65\textwidth}
    \begin{minipage}[c]{0.2\textwidth}
        % Placeholder for Logo
        \framebox[2cm][c]{\rule{0pt}{2cm}Logo} 
    \end{minipage}
    \begin{minipage}[c]{0.75\textwidth}
        {\LARGE \textbf{OMI CHAUHAN}} \\[2pt]
        Roll No.: 23MMB0A31 \\
        B.Tech in Metallurgy and Material Sciences \\
        National Institute of Technology, Warangal
    \end{minipage}
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
    \raggedleft
    \small
    \faPhone\ +91-9770845401 \\
    \faEnvelope\ \href{mailto:oc23mmb0a31@student.nitw.ac.in}{oc23mmb0a31@student.nitw.ac.in} \\
    \faEnvelope\ \href{mailto:omichauhan427@gmail.com}{omichauhan427@gmail.com} \\
    \faGithub\ \href{https://github.com/omichauhan-lgtm}{omichauhan-lgtm} \\
    \faLinkedin\ \href{https://www.linkedin.com/in/omichauhan/}{omichauhan}
\end{minipage}

\vspace{10pt}

% Education
\section*{EDUCATION}
\begin{tabularx}{\textwidth}{@{}X r@{}}
    \textbf{National Institute of Technology, Warangal} & 2023 -- 2027 \\
    \textit{B.Tech in Metallurgy and Material Sciences} & \\
    \multicolumn{2}{c}{} \\
    \textbf{Central Board of Secondary Education (Class XII)} & 2022 \\
    \textit{Higher Secondary} & 96\% \\
    \multicolumn{2}{c}{} \\
    \textbf{Central Board of Secondary Education (Class X)} & 2020 \\
    \textit{Secondary School} & 93\% \\
\end{tabularx}

% Experience - MODIFIED FOR HR (People Analytics focus)
\section*{EXPERIENCE}
\textbf{Rajputana Vehicles Pvt. Ltd.} \hfill May 2025 -- June 2025 \\
\textit{Data Analyst Intern} \hfill Madhya Pradesh, India
\begin{itemize}
    \item \textbf{People & Performance Analytics:} Used data to understand team performance and sales region efficiency.
    \item Developed dashboards to visualize human capital distribution and productivity metrics.
    \item Conducted segmentation analysis to identify training gaps and performance drivers.
    \item Presented findings to leadership to support organizational decision-making.
\end{itemize}

% LEADERSHIP - Moved UP for HR Role
\section*{LEADERSHIP & ORGANIZATIONAL EXPERIENCE}
\textbf{PR Team Head, Technozion} \hfill 2023 -- 2024 \\
\textit{Technical Fest, NIT Warangal}
\begin{itemize}
    \item Managed a team of 50+ students, coordinating communication and public relations for 10,000+ attendees.
    \item Resolved conflict situations and optimized team workflows to ensure smooth event execution.
    \item Strategized outreach campaigns that increased student participation by 20\%.
\end{itemize}

\vspace{5pt}

\textbf{Sponsorship Team Head, Springspree} \hfill 2023 -- 2024 \\
\textit{Cultural Fest, NIT Warangal}
\begin{itemize}
    \item Managed corporate sponsorships and partnerships, demonstrating strong stakeholder management and communication skills.
    \item Led negotiations with external vendors and partners to secure funding.
\end{itemize}

% Personal Projects
\section*{PERSONAL PROJECTS}
\textbf{AutoSight SaaS} \hfill 2024 \\
\textit{Market Analytics}
\begin{itemize}
    \item Built a platform for analyzing market demand, focusing on user behavior and segmentation.
\end{itemize}

\textbf{Credit Risk Intelligence} \hfill 2024 \\
\textit{Risk Assessment Tool}
\begin{itemize}
    \item Developed a system to predict risk factors, applying analytical thinking to evaluate profiles.
\end{itemize}

% Technical Skills - MODIFIED FOR HR
\section*{SKILLS AND INTERESTS}
\begin{itemize}
    \item \textbf{Soft Skills:} Team Leadership, Conflict Resolution, Event Management, Public Relations
    \item \textbf{Analytical Tools:} Python (Data Analysis), Excel, PowerPoint, SQL
    \item \textbf{Areas of Interest:} People Analytics, Organizational Behavior, Human Resources Management
\end{itemize}

% Achievements
\section*{ACHIEVEMENTS}
\begin{itemize}
    \item \textbf{JPMorgan Chase Forage Virtual Internship:} Gained insight into corporate workflows and financial technology.
\end{itemize}

\end{document}
